Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-10-11 proof.tex
alternative algo

To prove that the algorithm does compute the word with the best weight, we use the following invariant :
$$
<q_1, q_2> \notin Q \iff d_{bot} (q_1, q_2) = b_{bot} (q_1, q_2)
$$
In other words, a tuple $<q_1, q_2>$ is removed from the queue during an iteration only when $d_{bot}(q1, q2)$ has its minimal value.

>>>>

To prove that the algorithm does compute the word with the best weight, we use the following invariant :
$$
\<q_1, q_2> \notin Q \iff d_{\bot}(q_1, q_2) = b_{\bot}(q_1, q_2)
$$
In other words, a tuple $\<q_1, q_2>$ is removed from the queue during an iteration only when $d_{\bot}(q1, q2)$ has its minimal value.
